### 2015-07-10 narrative/proposed-work.tex
guiding principle 2.

\underline{Principle 1:} {\bf A knowledge-centric system design} that allows user knowledge  to
define data policies. Today Storage System and I/O layers are written in a
stove-pipe fashion, and quite often do not allow optimizations to take place.
We propose to re-design the layer in a highly integrated fashion where users
will place their intentions into the system and actions will statically and dynamically
take place to optimize for both the system and for individual
requests.

\underline{Principle 2}: {\bf Predictable performance and quality of data in the SSIO layer} needs to be
established so more science can be done on the exascale systems. Without
predictable performance, the I/O layer performance must be guessed by the
users, which quite often means that science is not performed well.

@@

One of the underlying principles of our approach is that we recognize that there are a small set
of important I/O patterns to optimize for~\cite{lofstead2011six,polte2009and,tian2011edo,tian2012system},
and our representative applications have worked with us on all of these I/O patterns. Throughout our project
we will continuously focus on creating research artifacts which can optimize these patterns on current generation through
exascale systems.  One important pattern is Checkpoint/Restarts (CR) and we will focus on optimizing these through our
research, and also using many of the important research techniques for using NVRAM and neighbor's NVRAM for storing 
the CR data. The migration and purging of this will be optimized by our SSIO layer, and we will have the user data intentions
signify the utility of CR data so that this data can be high-value but stored for short periods of time. The value of a chunk of data
from an object signifies it's importance to the users relative to the other chunks of their data.

>>>>

\underline{Principle 1:} {\bf A knowledge-centric system design} that allows user knowledge  to
define data policies. Today SSIO layers are written in a
stove-pipe fashion, and quite often do not allow optimizations to take place.
We propose to re-design the layers in a highly integrated fashion where users
will place their intentions into the system and actions will statically and dynamically
take place to optimize for both the system and for individual
requests.

\underline{Principle 2}: {\bf Predictable performance and quality of data in the SSIO layers} needs to be
established so science can be done on the exascale systems in a more efficient manner. Without
predictable performance, not only can the runs be slowed down because of contentions \cite{liu_hotstorage}, 
but also it affects key science decisions, e.g., how much data reduction should be performed.
It is clear that if a run is expected to be slow, an aggresive data reduction needs to be performed
so that science can be done in a timely fashion, which has been reflected in the XGC run (\S~\ref{sec:introduction})
the PI recently participated.

@@

One of the underlying principles of our approach is that we recognize that there are a small set
of important I/O patterns to optimize for~\cite{lofstead2011six,polte2009and,tian2011edo,tian2012system},
and our representative applications have worked with us on all of these I/O patterns. Throughout our project
we will continuously focus on creating research artifacts which can optimize these patterns on current generation through
exascale systems.  One important pattern is Checkpoint/Restarts (CR) and we will focus on optimizing these through our
research, and also using many of the important research techniques for using NVRAM and neighbor's NVRAM for storing 
the CR data. The migration and purging of this will be optimized by our SSIO layer, and we will have the user data intentions
signify the utility of CR data so that this data can be high-value but stored for short periods of time. The value of a chunk of data
from an object signifies its importance to the users relative to the other chunks of their data.
